From lutz@cs.iastate.edu  Fri May 21 16:46:04 1999
Return-Path: <lutz@cs.iastate.edu>
Received: from ren.cs.iastate.edu (lutz@ren.cs.iastate.edu [129.186.3.41])
	by css-1.cs.iastate.edu (8.9.0/8.9.0) with ESMTP id QAA09343
	for <simov@cs.iastate.edu>; Fri, 21 May 1999 16:46:03 -0500 (CDT)
Received: (from lutz@localhost)
	by ren.cs.iastate.edu (8.9.0/8.9.0) id QAA26741
	for simov; Fri, 21 May 1999 16:45:59 -0500 (CDT)
Date: Fri, 21 May 1999 16:45:59 -0500 (CDT)
From: Jack Lutz <lutz@cs.iastate.edu>
Message-Id: <199905212145.QAA26741@ren.cs.iastate.edu>
To: simov@cs.iastate.edu
Status: RO

\documentstyle[12pt]{article}
\setlength{\topmargin}{-.5in}
\setlength{\textheight}{9in}
\setlength{\textwidth}{6.5in}
\setlength{\oddsidemargin}{0in}
\setlength{\evensidemargin}{0in}
\newlength{\Num}
\setlength{\parindent}{0in}
\pagestyle{empty}
\begin{document}
\begin{center}
{\Large\bf Jack H. Lutz}
\end{center}

\vspace*{0.3in}
{\bf Address}

\vspace*{\smallskipamount}
Department of Computer Science 

Iowa State University

Ames, IA 50011

(515) 294-9941

lutz@cs.iastate.edu

\vspace*{\bigskipamount}
{\bf Experience}

\vspace*{\medskipamount}

Professor of Computer Science

Iowa State University, 1996 -- present

\medskip
Visiting Professor of Computer Science

Cornell University, Fall 1997

(on sabbatical from Iowa State University)

\medskip
Associate Professor of Computer Science

Iowa State University, 1992 -- 1996

\medskip
Assistant Professor of Computer Science

Iowa State University, 1987 -- 1992

\medskip
DIMACS Visiting Fellow (on sabbatical from Iowa State University)

\hangafter=1
\hangindent=0.3in
Center for Discrete Mathematics and Theoretical Computer Science, Rutgers,
Fall
1990

\vspace*{\medskipamount}
Graduate Research Assistant, Caltech 1984--1985, 1986--1987

\vspace*{\medskipamount}
Graduate Teaching Assistant, Caltech 1980--1987

\vspace*{\medskipamount}
Member of Technical Staff, TRW July 1985--October 1985

\hangafter=1
\hangindent=0.3in
Formal specification and formal verification of security properties of
computer systems.

\vspace*{\medskipamount}
Assistant Instructor, University of Kansas 1977--1980

\vspace*{\bigskipamount}
{\bf Research funding}

\vspace*{\smallskipamount}
Measure and Randomness in Computational Complexity, National
Science Foundation, 1997--2000.  (\$183,375)

\vspace*{\smallskipamount}
Presidential Young Investigator Award, National Science Foundation,
1991--1997.  (\$266,000)

\vspace*{\smallskipamount}
Matching Funds for Presidential Young Investigator Award, Rockwell International,
1991--1992, 1992--1993, 1993--1994, 1994--1995, 1995--1996.  (\$100,000)

\vspace*{\smallskipamount}
Matching Funds for Presidential Young Investigator Award, Microware
Systems Corporation, 1992--1993, 1993--1994, 1994--1995,
1995--1996.  (\$32,000)

\vspace*{\smallskipamount}
Matching Funds for Presidential Young Investigator Award, Amoco
Foundation, 1993--1994, 1994--1995.  (\$9,000)

\vspace*{\medskipamount}
IR \& D Project, Microelectronic Systems Division, Hughes Aircraft Company,
1990--1991.  (\$15,000)

\vspace*{\medskipamount}
Research Initiation Award, National Science Foundation, 1988--1991.  (\$37,906)

{\bf Education}

\vspace*{\smallskipamount}
Ph.D., Mathematics 1987

California Institute of Technology

\hangafter=1
\hangindent=0.3in
Thesis:  Resource-Bounded Category and Measure in Exponential
Complexity Classes

Major Advisor:  Alexander S. Kechris

Minor:  Computer Science

Minor Advisor:  Yaser S. Abu-Mostafa

\vspace*{\medskipamount}
M.S., Computer Science 1981

University of Kansas

Thesis:  Translations Between Indexings of Subrecursive Classes

\vspace*{\medskipamount}
M.A., Mathematics 1979

University of Kansas

\vspace*{\medskipamount}
B.G.S., Mathematics 1976

University of Kansas

\vspace*{\bigskipamount}
{\bf Research areas}

\vspace*{\smallskipamount} Computational Complexity, including 
structure of complexity classes, resource-bounded measure, and
probabilistic complexity.

\vspace*{\smallskipamount} Algorithmic Information and Randomness, 
including computational randomness, Kolmogorov complexity, 
computational depth, and games and prediction.

\vspace*{\bigskipamount}
{\bf Papers in refereed journals}

\begin{enumerate}
\item[{[1]}] Category and Measure in Complexity Classes, {\it SIAM
Journal on Computing\/} {\bf 19} (1990), pp.~1100--1131.
\item[{[2]}] Pseudorandom Sources for BPP, {\it Journal of Computer and
System Sciences\/} {\bf 41} (1990), pp.~307--320. (invited paper)
\item[{[3]}] An Upward Measure Separation Theorem, {\it Theoretical
Computer Science\/} {\bf 81} (1991), pp.~127--135.
\item[{[4]}]  On Independent Random Oracles, {\it Theoretical
Computer Science}, {\bf 92} (1992), pp.~301--307.
\item[{[5]}] Almost Everywhere High Nonuniform Complexity, {\it
Journal of Computer and System Sciences} {\bf 44} (1992), pp. 220--258.
 (invited paper)
\item[{[6]}] Circuit Size Relative to Pseudorandom Oracles (with
William~J. Schmidt), {\it Theoretical Computer Science} {\bf 107}
(1993), pp.~95--120.
(invited paper)
\item[{[7]}] On Languages With Very High Space--Bounded Kolmogorov 
Complexity (with Ronald V. Book), {\it SIAM Journal on Computing}
{\bf 22} (1993), pp.~395--402.
\item[{[8]}] A Pseudorandom Oracle Characterization of BPP, {\it SIAM
Journal on Computing} {\bf 22} (1993), pp.~1075--1086.
\item[{[9]}] An Observation on Probability versus Randomness with
Applications to Complexity Classes (with Ronald V. Book and Klaus W.
Wagner), {\it Mathematical Systems Theory\/} {\bf 27} (1994), pp. 201--209.
\item[{[10]}] Measure, Stochasticity, and the Density of Hard Languages (with
Elvira Mayordomo), {\it SIAM Journal on Computing\/} {\bf 23} (1994), pp.~
762--779.
\item[{[11]}] Computational Depth and Reducibility (with David W. Juedes and
James I. Lathrop), {\it Theoretical Computer Science\/} {\bf 132} (1994), 
pp. 37--70.
\item[{[12]}] The Complexity and Distribution of Hard Problems
(with David W. Juedes), {\it SIAM Journal on Computing\/} {\bf 24} 
(1995), pp.~279--295.
\item[{[13]}] Weak Completeness in E and ${\rm E}_2$ (with David W.
Juedes), {\it Theoretical Computer Science} {\bf 143} (1995),
pp.~149--158.
\item[{[14]}] The Global Power of Additional Queries to Random Oracles
(with Ronald V. Book and David M. Martin, Jr.),
{\it Information and Computation} {\bf 120} (1995), pp. 49--54.
\item[{[15]}] Weakly Hard Problems, {\it
SIAM Journal on Computing} {\bf 24} (1995), pp. 1170--1189.
\item[{[16]}] Completeness and Weak Completeness under
Polynomial--Size Circuits (with David W. Juedes), {\it Information
and Computation} {\bf 125} (1996), pp. 13--31.
\item[{[17]}] Cook versus Karp/Levin: Separating Completeness
Notions if NP is not Small (with Elvira Mayordomo),
{\it Theoretical Computer Science\/} {\bf 164} (1996), pp. 141--163.
\item[{[18]}] Observations on Measure and Lowness for $\Delta^{\rm
P}_{2}$, {\it Theory of Computing Systems} (formerly named
{\it Mathematical Systems Theory}) {\bf 30} (1997), pp. 429--442.
\item[{[19]}] Genericity and Randomness over Feasible Probability
Measures (with Amy K. Lorentz), {\it Theoretical Computer Science}
{\bf 207} (1998), pp. 245--259. (invited paper)
\item[{[20]}] Feasible Reductions to Kolmogorov--Loveland Stochastic
Sequences (with David L. Schweizer), {\it Theoretical Computer Science},
to appear.
\item[{[21]}] Equivalence of Measures of Complexity Classes (with
Josef M. Breutzmann), {\it SIAM Journal on Computing}, to appear.
\item[{[22]}] Recursive Computational Depth (with James I. Lathrop),
{\it Information and Computation}, to appear.
\item[{[23]}] One--Way Functions and Balanced NP, {\it Theoretical
Computer Science}, to appear.
\item[{[24]}] The Density of Weakly Complete Problems under
Adaptive Reductions (with Yong Zhao), {\it SIAM Journal on 
Computing}, to appear.
\item[{[25]}] Modeling Time-Bounded Prefix Kolmogorov Complexity
(with David W. Juedes), {\it Theory of Computing
Systems} (formerly named {\it Mathematical Systems Theory}),
to appear.
\end{enumerate}

\newpage
{\bf Invited book chapters}

\begin{enumerate}
\item[{[1]}] Kolmogorov Complexity, Complexity Cores, and the
Distribution of Hardness (with David W. Juedes), in O.
Watanabe (ed.), {\it Kolmogorov Complexity and Computational 
Complexity}, Springer-Verlag, 1992, pp.~43--65.
\item[{[2]}] Genericity and Randomness over Feasible Probability
Measures (with Amy K. Lorentz), in D.-Z. Du and K.-I. Ko (eds.),
{\it Advances in Algorithms, Languages, and Complexity}, Kluwer
Academic Publishers, 1997, pp. 171--187.
\item[{[3]}] The Quantitative Structure of Exponential Time,
in L. A. Hemaspaandra and A. L. Selman (eds.), {\it
Complexity Theory Retrospective II}, Springer-Verlag, 1997,
pp. 225--254.
\end{enumerate}

\vspace*{\bigskipamount}
{\bf Invited column}

\begin{enumerate}
\item[{[1]}] Twelve Problems in Resource-Bounded Measure (with
Elvira Mayordomo), in the Computational Complexity Column (E.
Allender, ed.), {\it Bulletin of the European Association for
Theoretical Computer Science} {\bf 68} (1999), to appear.
\end{enumerate}

\vspace*{\bigskipamount}
{\bf Conference papers}

\begin{enumerate}
\item[{[1]}] Resource--Bounded Baire Category and Small Circuits in
Exponential Space, {\it Proceedings of the Second Annual Structure 
in Complexity Theory Conference}
(Cornell University, Ithaca, NY, June~16--19, 1987), IEEE Computer Society Press,
1987, pp.~81--91.
\item[{[2]}] Pseudorandom Sources for BPP, {\it Proceedings of the 
Third Annual Structure in
Complexity Theory Conference} (Georgetown University, Washington, 
 D.C., June~14--17, 1988), IEEE Computer Society Press, 1988, pp.~175--180.
\item[{[3]}] Almost Everywhere High Nonuniform Complexity, {\it 
Proceedings of the Fourth
Annual Structure in Complexity Theory Conference} (University of
Oregon, Eugene, OR, June~19--22, 1989), IEEE Computer Society Press, 1989, pp.~37--53.
\item[{[4]}] Circuit Size Relative to Pseudorandom Oracles (with
William J. Schmidt), {\it 
Proceedings of the Fifth
Annual Structure in Complexity Theory Conference}
(Universitat Polit\`ecnica de Cat\-alun\-ya, Barcelona, Spain,
July~8--11, 1990), IEEE Computer Society Press, 1990, pp.~268--286.
\item[{[5]}] Additional Queries to Random and Pseudorandom Oracles
(with Ronald V. Book and Shouwen Tang),
{\it Proceedings of the Seventeenth International Colloquium on Automata, 
Languages, and Programming} 
(University of Warwick, Coventry, UK, July~16--20, 1990), 
Springer-Verlag, 1990, 
pp.~283--293.
\item[{[6]}] A Pseudorandom Oracle Characterization of BPP, {\it 
Proceedings of the Sixth
Annual Structure in Complexity Theory Conference} (University of
Chicago, Chicago, IL, June 30--July 3, 1991), IEEE Computer Society Press, 1991, 
pp.~190--195.
\item[{[7]}] On Complexity Classes and Algorithmically Random Languages
(with Ronald V. Book and Klaus Wagner), {\it Proceedings of the Ninth
Symposium on Theoretical Aspects of Computer Science} (Paris, France,
February 13-15, 1992), Springer-Verlag, 1992, pp.~319--328.
\item[{[8]}] On Languages With Very High Information Content
(with Ronald V. Book), {\it Proceedings of the Seventh Annual
Structure in Complexity Theory Conference} (Boston University, 
Boston, MA, June 22--25, 1992), IEEE Computer Society Press, 1992, pp. 255--259.
\item[{[9]}] Measure, Stochasticity, and the Density of Hard Languages
(with Elvira Mayordomo), {\it Proceedings of the Tenth Symposium on 
Theoretical Aspects of Computer Science} \linebreak (W\"{u}rzburg, Germany, 
February 25--27, 1993), Springer-Verlag, 1993, pp.~38--47.
\item[{[10]}] The Quantitative Structure of Exponential Time, {\it Proceedings
of the Eighth Annual Structure in Complexity Theory Conference\/} (San
Diego, CA, May 18--21, 1993), IEEE Computer Society Press, 1993, pp.~158--175.  (invited paper)
\item[{[11]}] Computational Depth and Reducibility (with David W.
Juedes and James I. Lathrop), {\em Proceedings of the Twentieth
International Colloquium on Automata, Languages, and Programming\/} (Lund
University, Lund, Sweden, July 5--9, 1993), Springer-Verlag, 1993, 
pp.~278--288.
\item[{[12]}] The Complexity and Distribution of Hard Problems 
(with David W. Juedes), {\it Proceedings of the $34^{th}$ IEEE
Symposium on Foundations of Computer Science\/} (Palo Alto, CA,
November 3--5, 1993), IEEE Computer Society Press, 1993, pp.~177--185.
\item[{[13]}] The Global Power of Additional Queries to Random Oracles
(with Ronald V. Book and David M. Martin, Jr.),
{\it Proceedings of the Eleventh Symposium on Theoretical Aspects of
Computer Science\/} (Caen, France, February 24--26, 1994), Springer--Verlag,
1994, pp. 403--414.
\item[{[14]}] Cook versus Karp/Levin: Separating Completeness 
Notions If NP is Not Small (with Elvira Mayordomo),
{\it Proceedings of the Eleventh Symposium on Theoretical Aspects of
Computer Science\/} (Caen, France, February 24--26, 1994), Springer--Verlag,
1994, pp. 415--426.
\item[{[15]}] Weakly Hard Problems, {\it Proceedings
of the Ninth Annual Structure in Complexity Theory Conference\/}
(Amsterdam, The Netherlands, June 28--July 1, 1994), IEEE Computer
Society Press, 1994, pp.~146--161.
\item[{[16]}] Completeness and Weak Completeness Under 
Polynomial--Size Circuits (with David W. Juedes),
{\it Proceedings of the Twelfth Symposium on Theoretical
Aspects of Computer Science\/} (Munich, Germany, March 2--4, 
1995), Springer-Verlag, 1995, pp.~26--37.
\item[{[17]}] A Small Span Theorem for P/Poly-Turing Reductions,
{\it Proceedings of the Tenth Annual Structure in Complexity
Theory Conference} (Minneapolis,
MN, June 19--22, 1995), IEEE Computer Society Press, 1995, pp. 324--330.
\item[{[18]}] Weakly Useful Sequences (with Stephen A. Fenner and
Elvira Mayordomo), {\it Proceedings of the Twenty-Second
International Colloquium on
Automata, Languages, and Programming} (Szeged, Hungary, July 10--14,
1995), Springer-Verlag, 1995, pp. 393--404.
\item[{[19]}] Observations on Measure and Lowness for
$\Delta^{\rm p}_{2}$, {\it Proceedings of the Thirteenth
Symposium on Theoretical Aspects of Computer Science} (Grenoble,
France, February 22--24, 1996), Springer-Verlag, 1996, pp. 87--97.
\item[{[20]}] Equivalence of Measures of Complexity Classes (with
Josef M. Breutzmann), {\it Proceedings of the Fourteenth Symposium 
on Theoretical Aspects of Computer Science} (L\"{u}beck, Germany,
February 27--March 1, 1997), Springer-Verlag, 1997, pp. 535--545.
\item[{[21]}] The Density of Weakly Complete Problems under
Adaptive Reductions (with Yong Zhao), {\it Proceedings of the 
Twelfth Annual IEEE Conference on Computational Complexity} 
(Ulm, Germany, June 24--27, 1997), IEEE Computer Society Press, 
1997, pp. 111--120.
\item[{[22]}] Recursive Computational Depth (with James I. Lathrop),
{\it Proceedings of the Twenty-Fourth International Colloquium on
Automata, Languages, and Programming} (Bologna, Italy, July 7--11, 
1997), Springer-Verlag, 1997, pp. 132--142.
\item[{[23]}] Resource-Bounded Measure, {\it Proceedings of the
Thirteenth Annual IEEE Conference on Computational Complexity}
(Buffalo, NY, June 15--18, 1998), IEEE Computer Society Press,
1998, pp. 236--248.
\item[{[24]}] Time-Bounded Prefix Kolmogorov Complexity
(with David W. Juedes), {\it Proceedings of the Thirty-Sixth Annual
Allerton Conference on Communication, Control, and Computing}
(Monticello, IL, September 23--25, 1998), University of Illinois
Press, 1998, pp. 703--712.
\item[{[25]}] Query Order and NP-Completeness (with Jack J. Dai),
{\it Proceedings of the Fourteenth Annual IEEE Conference on 
Computational Complexity} (Atlanta, GA, May 4--6, 1999), IEEE
Computer Society Press, 1999, pp. 142--148.
\end{enumerate}

\vspace*{\bigskipamount}
{\bf Papers under review}

\begin{enumerate}
\item[{[1]}] Query Order and NP-Completeness (with Jack J. Dai),
submitted to {\it Information and Computation}.
\end{enumerate}

\vspace*{\bigskipamount}
{\bf Invited tutorials}

\begin{enumerate}
\item[{[1]}] ``Resource-Bounded Measure,'' Logic Colloquium '96:
European Summer Meeting of the Association for Symbolic Logic,
San Sebastian, Spain, July 9--15, 1996.  (three hours)
\item[{[2]}] ``Kolmogorov Complexity and its Applications,'' 
Fourth International Colloquium on Grammatical Inference,
Ames, IA, July 12--14, 1998.  (two hours)
\end{enumerate}
 
\vspace*{\bigskipamount}
{\bf Lectures at meetings that do not publish formal proceedings}

\begin{enumerate}
\item[{[1]}] ``Measure-Theoretic Pseudorandomness:  Robustness of the
Notion,'' 1990 AAAI Spring Symposium on Theory and Applications of
Minimal-Length Encoding, Stanford University, Stanford, CA,
March~27--29, 1990.
\item[{[2]}] ``A Pseudorandom Oracle Characterization of BPP,'' Workshop
in Structural Complexity Theory, University of California, Santa
Barbara, CA, March~30--31, 1990. (invited talk)
\item[{[3]}] ``Intrinsically Pseudorandom Sequences,'' DIMACS 
Workshop on Structural Complexity and Cryptography, Rutgers
University, Piscataway, NJ, December~3--6, 1990.
\item[{[4]}] ``Measure (and Category) in Complexity Classes,'' Workshop on 
Structurally Related Complexity Theory, Fourth European Summer School
on Logic, Language, and Information, University of Essex, Colchester, UK,
August 17--28, 1992. (invited talk)
\item[{[5]}] ``The Structure of Exponential Time,'' Workshop on 
Structurally Related Complexity Theory, Fourth European Summer School
on Logic, Language, and Information, University of Essex, Colchester, UK,
August 17--28, 1992. (invited talk)
\item[{[6]}] ``The Utility and Depth of Information,'' Seminar on
Descriptional Complexity, International Conference and Research Center
for Computer Science, Schloss Dagstuhl, Germany, May 3--7, 1993.
(invited talk)
\item[{[7]}] ``Feasible Martingales, Weak Completeness, and Strong
Hypotheses,''  Seminar on Structure and Complexity,
International Conference and Research Center for Computer Science, 
Schloss Dagstuhl, Germany, February 14--18, 1994.
\item[{[8]}] ``Observations on Measure and Lowness for
$\Delta^{\rm P}_{2}$,'' American Mathematical Society Annual
Meeting for the Southeastern Section, Special Session on
Complexity Theory, Greensboro, NC, November 17--18, 1995.
(invited talk)
\item[{[9]}] ``Equivalence of Measures of Complexity Classes,''
Workshop on Information and Randomness in Complexity Classes,
International Conference and Research Center for Computer
Science, Schloss Dagstuhl, Germany, July 15--19, 1996.
\item[{[10]}] ``Equivalence of Measures of Complexity Classes,''
Seminar on Structure and Complexity,
International Conference and Research Center for Computer
Science, Schloss Dagstuhl, Germany, September 30--October 4, 1996.
\item[{[11]}] ``Genericity and Randomness over Feasible Probability
Measures,'' Workshop on Languages, Algorithms, and Complexity 
(Celebrating the Sixtieth Birthday of Professor Ronald V. Book),
University Of Minnesota, Minneapolis, MN, April 12, 1997.
(invited talk)
\item[{[12]}] ``Resource-Bounded Measure,'' Meeting on Logic,
Computability, and Complexity, National Research Institute for 
Mathematics and Computer Science (CWI),
Amsterdam, The Netherlands, March 5--7, 1998. (invited talk)
\end{enumerate}

\vspace*{\bigskipamount}
{\bf Recent lectures at universities}

\begin{enumerate}
\item[{[1]}] ``Randomness and Prediction,'' ENT Distinguished
Lecture, Russ College of Engineering and Technology, Ohio
University, February 4, 1997.
\item[{[2]}] ``Weak Completeness and Strong Hypotheses,''
Computer Science Colloquium, Iowa State University, October
23, 1997.
\item[{[3]}] ``Weak Completeness and Strong Hypotheses,''
Buffalo-Rochester
Theory Seminar, Department of Computer Science, University
of Rochester, November 14, 1997.
\item[{[4]}] ``Weak Completeness and Strong Hypotheses,''
Theory Seminar, Department of Computer Science, Cornell
University, November 17, 1997.
\item[{[5]}] ``Measure in Complexity Classes,''
Caltech Logic Seminar, Department of Mathematics,
California Institute of Technology, January 14, 1998.
\end{enumerate}

\vspace*{\bigskipamount}
{\bf Teaching}

\vspace*{\smallskipamount}
Courses taught at Iowa State University:

\hangindent=0.3in
\hangafter=0
\vspace*{\smallskipamount}
Undergraduate:

\hspace*{0.6in} Computer Science 330 (Discrete Computational
Structures) Spring
\hangindent=0.9in
\hangafter=1
1988 (two sections), Fall 1988, Spring 1989, Fall 1989, Spring 1990, Fall
1991, Spring 1992, Fall 1992, Spring 1993, Fall 1993, Spring
1994, Spring 1995, Spring 1996, Fall 1998

\hangindent=0.9in
\hangafter=1
\hspace*{0.6in} Computer Science 331 (Theory of Computing) Spring 1995, Fall 1995 \\

\vspace*{-0.15in}
\hangindent=0.3in
\hangafter=0
Graduate:

\hangindent=0.9in
\hangafter=1
\hspace*{0.6in} Computer Science 531 (Theory of Computation)
Fall 1987, Fall 1988, Fall 1992, Spring 1997

\hangindent=0.9in
\hangafter=1
\hspace*{0.6in} Computer Science 532 (Theoretical Foundations) Spring 1991

\hangindent=0.9in
\hangafter=1
\hspace*{0.6in} Computer Science 631 (Computational Complexity)
Fall 1989, Fall 1991, Fall 1994, Spring 1997, Fall 1998

\hangindent=0.9in
\hangafter=1
\hspace*{0.6in} Computer Science 633 (Randomness in Computation)
Spring 1994, Spring 1996, Spring 1998

\vspace*{\medskipamount}
\hangindent=0.6in
\hangafter=1
Served as mentor for Freshman Honors Program (University Studies 290H)
Spring 1988, Spring 1992, Spring 1997, Spring 1998

\vspace*{\medskipamount}
\hangindent=0.6in
\hangafter=1
Taught special topics course (Computer Science 490/590: Information,
Program Size, Data Compression, and Forecasting) Fall 1993

\vspace*{\medskipamount}
\hangindent=0.6in
\hangafter=1
Conducted Information and Complexity Seminar (Computer
Science 610) Fall 1987, 
Spring 1988, Summer 1988, Fall 1988, Spring
1989, Summer 1989, Spring 1990, Spring 1991, 
Summer 1991, Fall 1991,
Spring 1992, Fall 1992, Spring 1993, Spring 1994,
Fall 1994, Spring 1995, Fall 1995, Spring 1996,
Spring 1997, Spring 1998, Fall 1998, Spring 1999

\vspace*{\medskipamount}
Ph.D. degrees supervised and completed at Iowa State University:

\begin{enumerate}
\item[{[1]}]
David W. Juedes (Ph.D., 1994: ``The Complexity and Distribution of
Computationally Useful Problems''), Assistant Professor of Computer
Science, Ohio University, Athens, Ohio.
\item[{[2]}]
Josef M. Breutzmann (Ph.D., 1996: ``The Complexity of Parameters for
Probabilistic and Quantum Computation''), Professor of
Computer Science and Mathematics, Wartburg College, Waverly, IA.
\item[{[3]}]
James I. Lathrop (Ph.D., 1997: ``Computing and Evolving
Variants of Computational Depth''), Scientist, NewMonics, Inc.,
Ames, IA; Affiliate Assistant Professor of Computer Science,
Iowa State University, Ames, IA.
\end{enumerate}

\vspace*{\smallskipamount}
M.S. degrees supervised and completed at Iowa State University:

\begin{enumerate}
\item[{[1]}]
Robert Matthews (M.S., 1989:  ``Iterative Computation of Rapidly
Growing Functions''), Assistant Professor, Department of Mathematic
and Computer Science, Armstrong State College, Savannah, Georgia,
1989--1995.  Now a Ph.D. student, Department of Computer Science,
College of William and Mary, Williamsburg, VA.
\item[{[2]}]
David W. Juedes (M.S., 1990: ``Hard and Weakly Hard Problems Under
Nonuniform Reductions''), continued for Ph.D., listed above.
\item[{[3]}]
William J. Schmidt (M.S., 1991: ``Circuit Size Relative to
Pseudorandom Oracles''), Development Staff Member, IBM, Rochester, MN.
\item[{[4]}]
Owen Reynolds (M.S., 1993: ``Relative to a Random Oracle, co-NP
Is Not Contained in IP/Poly'').
\item[{[5]}]
J. Andrew Edwards (M.S., 1993: ``Pseudorandom Generators and
Structural Complexity''), Software Engineer, NewMonics, Inc.,
Ames, IA.
\item[{[6]}]
James I. Lathrop (M.S., 1994: ``Compression Depth and the Behavior of
Cellular Automata''), continued for Ph.D., listed above.
\item[{[7]}]
Yong Zhao (M.S., 1995: ``$(\alpha, \beta)$-Randomness and Computational 
Depth''), Software Engineer, Nationwide Insurance, Columbus, OH.
\item[{[8]}]
Borislov Simov (M.S., 1995: ``Tests for Poly-Random
Collections''), Ph.D. student, Iowa State University.
\end{enumerate}

\vspace*{\smallskipamount}
External memberships on Ph.D. committees at other universities:

\hangindent=0.3in
\hangafter=0
\vspace*{\medskipamount}
Elvira Mayordomo (Ph.D., Computer Science, 1994: ``Contributions
to the Study of Resource-Bounded Measure,'' Universitat
Polit\`{e}cnica de Catalunya, Barcelona, Spain), Associate
Professor of Computer Science, University of Zaragoza,
Zaragoza, Spain.

\hangindent=0.3in
\hangafter=0
\vspace*{\medskipamount}
Martin Strauss (Ph.D., Mathematics, 1995: ``Measure in Feasible
Complexity Classes,'' Rutgers University, New Brunswick, New 
Jersey), Senior Technical Staff Member, AT\&T Labs, Florham
Park, NJ.

\hangindent=0.3in
\hangafter=0
\vspace*{\medskipamount}
Yongge Wang (Ph.D., Mathematics, 1996: ``Randomness and 
Complexity,'' University of Heidelberg, Heidelberg,
Germany), Postdoctoral Research Associate, Department
of Computer Science, University of Wisconsin at Milwaukee,
Milwaukee, WI.

\hangindent=0.3in
\hangafter=0
\vspace*{\medskipamount}
Sebastiaan A. Terwijn (Ph.D., Mathematics, 1998: 
``Computability and Measure,'' University of Amsterdam,
Amsterdam, The Netherlands), TMR Marie Curie Postdoctoral
Fellow, Mathematics Institute, University of Munich, Munich,
Germany.

\vspace*{\medskipamount}
Graduate students currently supervised at Iowa State
University:

\vspace*{\smallskipamount}

\hangindent=0.6in
\hangafter=1
\hspace*{0.3in} Jack J. Dai (Ph.D., Probability and Randomness),
completion expected May, 2000.

\vspace*{\smallskipamount}

\hangindent=0.6in
\hangafter=1
\hspace*{0.3in} Amy Lorentz (M.S., Randomness and Genericity),
completion expected May, 1999.

\vspace*{\smallskipamount}

\hangindent=0.6in
\hangafter=1
\hspace*{0.3in} Sridhar Srinivasan (M.S., Information and
Complexity), completion expected August, 1999.

\hangindent=0.6in
\hangafter=1
\hspace*{0.3in} Vikram Mhetre (M.S., Complexity and
Randomness), completion expected August, 1999.

\hangindent=0.6in
\hangafter=1
\hspace*{0.3in} Richard Miller (M.S., Complexity and 
Measure), completion expected December, 1999.


\vspace*{0.2in}
\hangindent=0.3in
\hangafter=1
Supervised the research of Sebastiaan A. Terwijn, a
Ph.D. student at the University of Amsterdam, during his
four-month stay at Iowa State University (August, 1995 -
November, 1995) on a Fulbright Scholarship.

\hangindent=0in
\vspace*{\bigskipamount}
{\bf Awards}

\vspace*{\smallskipamount}
Presidential Young Investigator, National Science Foundation, 1991

Excellence in Teaching Award, Iowa State University, 1990

Bohnenblust Travel Prize, Caltech, 1983

Florence Black Teaching Award, University of Kansas, 1978

\vspace*{\bigskipamount}
{\bf Memberships}

\vspace*{\smallskipamount}
Association for Computing Machinery

Special Interest Group on Algorithms and Computation Theory

European Association for Theoretical Computer Science

Association for Symbolic Logic

American Mathematical Society

Mathematical Association of America

Society for Industrial and Applied Mathematics

\vspace*{\bigskipamount}
{\bf Refereeing}

{\em SIAM Journal on Computing}

{\em Theoretical Computer Science}

{\em Journal of Computer and System Sciences}

{\em Information Processing Letters}

{\em Journal of Complexity}

{\em IEICE Transactions on Information and Systems}

IEEE Symposium on Foundations of Computer Science

IEEE Conference on Computational Complexity

Symposium on Theoretical Aspects of Computer Science

\hangafter=1
\hangindent=.3in
International Symposium on Mathematical Foundations of
Computer Science

U.S.-Japan Cooperative Science Program (National Science Foundation)

Idaho Specific Research Grant Program

International Science Foundation Long-Term Research Grants

\vspace*{\bigskipamount}
{\bf Other external service}

\hangafter=1
\hangindent=0.3in
Member of Program Committee, Eighth IEEE Structure in Complexity Theory
Conference, San Diego, CA, 1993.

\hangafter=1
\hangindent=0.3in
Member of Committee of Visitors for oversight review of Theory
of Computing Program, National Science Foundation, 1993.

\hangafter=1
\hangindent=0.3in
Member of Program Committee, Eleventh IEEE Conference on
Computational Complexity, Philadelphia, PA, 1996.

\hangafter=1
\hangindent=0.3in
Organizer (with Klaus Ambos-Spies and Ronald V. Book) of Workshop
on Information and Randomness in Complexity Classes,
International Conference and Research Center for Computer
Science, Schloss Dagstuhl, Germany, July 15--19, 1996.

\hangafter=1
\hangindent=0.3in
Member of Review Panel, National Science Foundation.

\hangafter=1
\hangindent=0.3in
Member of Program Committee, Fourteenth Symposium on 
Theoretical Aspects of Computer Science, Paris,
France, 1998.

\vspace*{\bigskipamount}
{\bf Internal service}

\vspace*{\smallskipamount}
\hangindent=0.3in
\hangafter=1
Computer Science Department Director of Graduate Education, 1998--1999

\hangafter=1
\hangindent=0.3in
Liberal Arts and Sciences Dean Search Committee, Fall 1998

\hangafter=1
\hangindent=0.3in
Computer Science Department Graduate Committee, 1988--1999; Chair 1996--1998

\hangafter=1
\hangindent=0.3in
Computer Science Department Teaching Evaluation Committee, 1997--1999

\hangafter=1
\hangindent=0.3in
Computer Science Department Faculty Search Committee, 1990--1991, 1995--1996,
1996--1997

\hangafter=1
\hangindent=0.3in
Computer Science Department Promotion and Tenure Steering Committee, 1996--1997

\hangafter=1
\hangindent=0.3in
Fourth Annual Faculty Conference, Grinnell, IA, March 22--23, 1996

\hangafter=1
\hangindent=0.3in
Computer Science Department Ad Hoc Committee on Long Range Strategic
Planning, 1994--1995

\hangafter=1
\hangindent=0.3in
Computer Science Department Ad Hoc Committee on Outcomes Assessment,
1991--1992, 1994--1995

\hangafter=1
\hangindent=0.3in
Computer Science Department Ad Hoc Committee on Collaborative
Efforts in Software Engineering, 1994--1995

\hangafter=1
\hangindent=0.3in
Computer Science Department Faculty Advisory Committee for
Review of Department Executive Officer, Fall 1994

\hangafter=1
\hangindent=0.3in
Computer Science Department Ad Hoc Committee on $25^{\rm th}$ Anniversary,
1993--1994

\hangafter=1
\hangindent=0.3in
Computer Science Department Ad Hoc Committee on Governance, 1989--1990

\hangafter=1
\hangindent=0.3in
Science and Humanities Ad Hoc Committee on `White Paper' for High
School Mathematics Requirements, Fall 1988

\hangafter=1
\hangindent=0.3in
Computer Science Department Undergraduate Committee, 1987--1988


\end{document}


